%%%%%%%%%%%%%%%%%   RABEA READ ME!!! %%%%%%%%%%%%%%%%%%%%%%
%
% I am changing a few things just to clean it up. 
% Since we will mostly be working in the latex files from now on, most of our comments should be here too. 
% I will be moving towards only having the latex files in the github repository.
% In order to differentiate between old comments, and between your comments and mine, I will begin all my comments particular to this document with `Thomas:' (unless it appears in `THOMAS GENERAL NOTES SECTION')
% If you answer one of my comments with your own, please INDENT (just hit tab once or twice) and start with `Rabea:'  . . . This should make it easier to read these, thank you for your patience.
%
%
% ALSO: Please don't be angry, I made a lot of suggestions and not too many corrections. All in all I think your other cover letters were better at conveying why you would be a good fit. Perhaps we can talk over the phone about this soon? Love you!

%%%%%%%%%%%%%%%%%%%%%%%%% 		CHECKLIST		%%%%%%%%%%%%%%%%%%%%%%%%%
%
% 		Did you:
%				1) Check for the correct date?
%				2) Check that the recipeient's name and address were correct?
%				3) Copy into Word for spelling errors?
%				4) Use a word counter online to check for overused language?


%%%%%%%%%%%%%%%%%%%%%		 DOCUMENT CLASS, PACKAGES 		%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[11pt,a4paper,sans]{moderncv}

\usepackage{float}
\usepackage{caption}
\usepackage{fancyhdr}
\usepackage{setspace}
\usepackage{verbatim}
\usepackage{xcolor} % Added this for highlights
\usepackage[normalem]{ulem} % Added this for strikeouts
\usepackage[scale=0.8, top = 1.8cm, bottom = 3cm]{geometry}                  

%%%% FIX THIS SO IT LOOKS NICER
% Thomas: Do you actually want to change the format of the footer or is the above comment outdated?


%%%%%%%%%%%%%%%%%%%%%%%%%%% 		FOOTER, HEADER, MODERNCV INPUTS		 %%%%%%%%%%%%%%%%%%%%%%%%%%%

\fancypagestyle{titlepage}{
\fancyhead{}
\fancyfoot[CE, CO]{\textcolor{gray}{Via Ramarini 32, Monterotondo RM, 00015 \thinspace\thinspace $\bullet$ \thinspace\thinspace\mobilephonesymbol +39~(388)~059~1507 \thinspace\thinspace $\bullet$ \thinspace\thinspace \faSkype \thinspace\thinspace \href{skype:rabea.jesser}{rabea.jesser} \thinspace\thinspace \thinspace\thinspace \emailsymbol \href{mailto:rabeajesser@web.de}{rabeajesser@web.de} \thinspace\thinspace $\bullet$ \thinspace\thinspace \faLinkedin \thinspace\thinspace \href{https://www.linkedin.com/in/rabeajesser/}{https://www.linkedin.com/in/rabeajesser/}}}}
\name{\vspace{-5mm}Rabea Jesser}{\vspace{3mm}}
\moderncvstyle{casual}                             
\moderncvcolor{blue}
\thispagestyle{titlepage}
% DONT FORGET TO UPDATE THIS!
\recipient{National Bioenergy Center}{National Renewable Energy Laboratory\\15013 Denver West Parkway, Golden, CO 80401}
% DONT FORGET TO UPDATE THIS OR USE \today
\date{\today}
%%%%% IF YOU KNOW WHO YOU'RE SENDING THIS TO THEN GIVE THEIR NAME
\opening{Dear Dr. Calvin Henard,}
\closing{Sincerely,}
\enclosure[Note]{M.Sc. Thesis, B.Sc., references and a more complete CV can also be sent upon request.}   


%%%%%%%%%%%%%%%%%%%% NOTES FOR CONTEXT OF LETTER, INFO ON ADDRESSEE %%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
\large
\centerline{\textbf{\underline{Adapting Methane with Yeast - Calvin Henard}}}
\vspace{2.5mm}
\normalsize
{\doublespacing
\begin{enumerate}
\item Methylomicrobium alcaliphilum 20ZR as platform for production of fuels and value-added chemicals
\item Model biochemical pathways
\item Uses expertise in molecular biology and microbial genetics to develop algal, yeast, and bacterial biocatalyst for conversion of renewable substrates to biofuels and bioproducts
\item Methane biocatalysis to fuels and chemicals
\begin{enumerate}
\item Methanogenesis and anaerobic digestion of lignocellulosic biomass and waste streams % Thomas: these were tabbed so I did not know if you wanted them indented or not, assumed former.
\item Advanced genetic tool development for industrial microbes
\item Isolation of environmental microbes with industrially promising characteristics
\item The role of nitric oxide (NO) signaling in algal lipid accumulation
\end{enumerate}
\end{enumerate}
}
\vspace{5mm}\centerline{\noindent\rule{8cm}{0.4pt}}\vspace{5mm}


%%%%%%%%%%%%%%%% 			THOMAS GENERAL NOTES 			%%%%%%%%%%%%%%%%%%%%%%%%%%

% As you can tell I changed the outline of this document to make it easier to see comments/suggestions without the aid of a pdf
% I found the best way to insert comments within the paragraphs was to add a `%' after the end of the sentence(s) you are referring to and then use another `%' for the actual comment
% You can also probably tell I have yet to make any serious changes to the actual text . . . I will when I am not so tired/about to go to bed . . .  Please forgive me!!!!
% for added text, just so you can see it, I will highlight it in green, you can highlight yours in yellow (https://tex.stackexchange.com/questions/141569/highlight-textcolor-and-boldface-simultaneously#319000)
% for removed text I will strike it out (https://tex.stackexchange.com/questions/23711/strikethrough-text#23712)
% Whether you reject or accept my edits, get rid of the formatting. I only want to see your edits, not my left-over ones. So when I get this back, at least w.r.t. to the text I should only see your highlights and strikeouts, not mine.



%%%%%%%%%%%%%%%%%%%%%		BEGIN DOCUMENT		%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

       
\makelettertitle
\begin{spacing}{1.15}

Having seen the destructive consequences of our overreliance on fossil fuels, I have an abiding desire to contribute towards the development of alternative fuels that would allow our society to prosper without detriment to the planet. % 
% Ok . . . the balance you have to strike here in the first paragraph is 1) You want to grab their attention and make sure they remember you; 2) You want to make sure they know your passionate; 3) You want them to IMMEDIATELY see why they would want you; and 4) You want to make sure that you do not sound as if you are lying/exaggerating to suck up to them. I am not sure how to do all of these any better than you have but I would say we change the first sentence. I need time to think about it . . .
NREL's National Bioenergy Center, with its dedication to finding sustainable, secure transportation systems, represents the perfect fit for my ambitions and passions. %
% Again, this is about why you would want them, let's save this for the last paragraph.
Likewise, having focused on organisms that could be used for the generation of biofuels or secondary metabolites, I believe my skills and background make me an excellent candidate for NREL.\par\vspace*{1mm} %
% This sentence is ok but the first paragraph is really your opportunity to impress them. Looking at other cover letters you wrote, like the 5th draft of Gevo or the 2nd draft of the Mycotechnology cover letter, the biggest differences I see are that: 1) You give a good overview of your skills in background and 2) You focus on why they would want you, not the other way around.

During my bachelor thesis I gained insight into the cultivation of \textit{Nannochloropsis oceanica} and \textit{Phaeodactylum tricornutum} and during my master thesis I successfully cultivated and processed Synechocystis sp. PCC 6803 {\href{https://www.ncbi.nlm.nih.gov/pubmed/29517395}{\textcolor{blue}{{\textit{(Publication)}}}}}. %
% This first sentence feels `dry': it reads more like a shopping list than a list of accomplishments. When I have more time I will work with you on how to `spice' this up.  
These experiences have left me well prepared to work preparing and cultivating both algae and cyanobacteria. %
% Again, same as previous sentence, this seems a little boring, you want the eyes to be popping out of their heads as they read about what a fucking badass scientist you are! (And you ARE a badass scientist!)	
The wide array of lectures and courses I took in biochemistry, organic chemistry, molecular biology and microbiology has also left me with a solid foundation to learn and develop new procedures and protocols in the lab.\par\vspace*{1mm} %
% I like this sentence, you quickly cover what you learned and you directly state how it could help.

As part of a student competition called iGEM (international Genetically Engineered Machine), I learned how to work independently and cooperate with an interdisciplinary team of 20 students. %
% This sentence also seems a bit plain, iGEM is a big deal (or you can make it sound that way) so you should really talk it up! The Gevo Draft 5 is a good example of how you can immediately connect your work with iGEM to contributions you could make at NREL, and then once you have them `hooked' you can elaborate on what you learned.
To improve team coordination and communication I expanded my proficiency in handling Microsoft office suite and gene analysis softwares (Geneious, Snapgene) and learned how to set up and organize databases (FileMaker) and use an internal wiki for accurate and reliable data storage. %
% This is a good sentence for detailing the skills you learned in iGEM, all that's missing is why NREL should be glad you have them/how you could use them to help NREL
Through iGEM and my theses I learned to clearly communicate results to my team and a wider audience using oral presentations and a {\href{http://2015.igem.org/Team:Freiburg}{\textcolor{blue}{\textit{website}}}}. %
% It's good that you brought light to an accomplishment here, it's not so good that this is such a stand-alone sentence; why do they care? how will you bring this to NREL?
To further hone this skill I attended a professional course on proper presentation.\par\vspace*{1mm} %
% Again, this is so, so, so short! And it's great you went to this course, but how does it help them?

My current team at the European Molecular Biology Laboratory (EMBL) \sout{comprises}\colorbox{green}{consists of} two members, giving me ample experience in the basic organization and daily maintenance of running a lab. %
% This is good, you explain a situation and how it relates to them
During my time here I have acquired a broad range of responsibilities and have learned to balance multiple projects while managing my time to keep ahead of deadlines. %
% Good, but by listing a few of these responsibilities I think it could become better
Within the first few months at EMBL my job description changed quite dramatically and I had to quickly learn techniques that were new to both my supervisor and me. %
% Ok, but what were some of these techniques? You Could also drop the part about your job description changing and use the space to talk about responsibilities and techniques
Due to the reshaping I also started working in a BSL2 environment and am thus aware of the importance of stringently following safety guidelines and maintaining a safe working environment.\par\vspace*{1mm} %
% Ok, but is this a concern for them? If not, then reduce this sentence and use the space to write about things they want to hear.

Besides the experience I collected in different laboratory environments over time, I bring excellent interpersonal, organizational and communication skills shaped by a range of volunteering activities. %
% I would move this to the end of the previous paragraph.
Given my skillset I believe I could make valuable contributions to NBC's team and it would be an honor to contribute to your research into algal biofuels. %
% I would combine this with what you mentioned in the opening paragraph (second sentence, not first) and use the new space in the first paragraph for other stuff.
If you agree, I would appreciate the opportunity to discuss the position and my potential contributions in more detail.  %
% This is basic and probably wont change much across papers
Thank you for your time and consideration, I look forward to hearing from you. %
%  

\end{spacing}
%\vspace*{1mm} 
\makeletterclosing
\end{document}
