\documentclass[11pt,a4paper,sans]{moderncv}

\usepackage{float}
\usepackage{caption}
\usepackage{fancyhdr}
\usepackage{setspace}
\usepackage{verbatim}
\usepackage[scale=0.8, top = 1.6cm, bottom = 2cm]{geometry}

\moderncvstyle{casual}                             
\moderncvcolor{blue}                               


%%%% FIX THIS SO IT LOOKS NICER
\fancypagestyle{titlepage}{
\fancyhead{}
\fancyfoot[CE, CO]{\textcolor{gray}{Via Ramarini 32, Monterotondo RM, 00015 \thinspace\thinspace $\bullet$ \thinspace\thinspace\mobilephonesymbol +39~(388)~059~1507 \thinspace\thinspace $\bullet$ \thinspace\thinspace \faSkype \thinspace\thinspace \href{skype:rabea.jesser}{rabea.jesser} \thinspace\thinspace \thinspace\thinspace \emailsymbol \href{mailto:rabeajesser@web.de}{rabeajesser@web.de} \thinspace\thinspace $\bullet$ \thinspace\thinspace \faLinkedin \thinspace\thinspace \href{https://www.linkedin.com/in/rabeajesser/}{https://www.linkedin.com/in/rabeajesser/}}}}


\name{\vspace{-5mm}Rabea Jesser}{\vspace{3mm}}

\begin{document}

%HORIZON
%commitment to learning, EXAMPLE ABOUT ILLUSTATOR, FILEMAKER, NEW  PROTOCOLS
%strong problem-solving skills, MENTION TROUBLE SHOOTING (QUANTIFICATION?)
%effective and clear communication skills, 
%meticulous attention to detail, MENTION THIS SOMEWHERE
%understanding of biology and chemistry, OBVIOUSLY?
%dedication to maintaining a safe, clean, and efficient work environment. MENTION EFFICIENT SOMEWHERE 
%Minimum of an AA degree. Preferred is a B.S. degree in biology, chemistry or a closely related field with 3 years’ experience. GOT THAT
%Knowledge of laboratory terminology and equipment. GOT THAT
%Excellent interpersonal and process-management skills. GOT  THAT
%Analytical and critical-thinking skills. MENTION THIS
%Aptitude for data analysis and statistics and the application of those results. MENTION THAT I AM ABLE TO ANALYZE DATA
% Strong Knowledge of Microsoft Excel, Word and PowerPoint. 

%scientifically-proven, field-tested products, desire to develop sustainable technologies, based on solid scientific principles


%%%%%%%%%%%%% 			THOMAS NOTES 			%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\thispagestyle{titlepage}

\recipient{Horizon Ag-Products, LP}{1450 Infinite Drive\\Louisville, CO 80027\vspace{-2mm}}
%%%% DONT FORGET TO UPDATE THIS OR USE \today
\date{\today}
%%%%% IF YOU KNOW WHO YOU'RE SENDING THIS TO THEN GIVE THEIR NAME
\opening{Dear Horizon Ag representative,\vspace{-2mm}}
\closing{Sincerely,\vspace*{-4mm} }
%\enclosure[Note]{Reference contacts and/or letters of reference will be sent upon request.}          
\makelettertitle
\begin{spacing}{1.15}

Given my strong scientific background and organizational skills, I would make an excellent addition to the Horizon team as a Research Technician and relish the opportunity to help develop research-driven, thoroughly tested products to advance sustainable agriculture. After a B.Sc. in Biology and participation in the iGEM (international Genetically Engineered Machine) competition, I received a M.Sc. in Biology before working with the European Molecular Biology Laboratory (EMBL) in Rome. Across various research projects I have worked both independently and as part of a team, gaining strong problem-solving skills, precise attention to detail and excellent communication skills. Furthermore, I have a proven ability to adapt to new challenges, am eager to learn and am dedicated to providing a functioning, clean, and efficient work environment.\par\vspace*{2mm}

During my B.Sc. thesis I worked with \textit{Nannochloropsis oceanica} and \textit{Phaeodactylum tricornutum} while for my M.Sc. thesis I cultivated Synechocystis sp. PCC 6803 {\href{https://www.ncbi.nlm.nih.gov/pubmed/29517395}{\textcolor{blue}{{\textit{(Publication)}}}}}. Through these experiences I developed excellent analytical and critical thinking skills and became well-versed in gathering, analyzing and recording scientific data. The wide array of lectures I took in plant sciences, translational biology and microbiology has meanwhile left me with a solid foundation to understand nutrient flows in plants, analyze cause and effect relationships and implement published methods. More generally, I have consistently shown I can quickly learn new procedures and protocols. For instance, during a reorganization of my current lab, I established protocols for the production and quantification of viral vector tools in mammalian cell culture using techniques that were new to both my supervisor and me. I also began working in a BSL2 environment and am aware of the importance of stringently following safety guidelines as well as maintaining a clean, safe and efficient working environment.\par\vspace*{2mm}

Outside of the lecture hall, iGEM gave me the chance to work within an interdisciplinary team of 20 students and to adapt new protocols in a team environment. iGEM also provided an opportunity to hone my skills in the daily upkeep of a lab, including ensuring the availability of reagents, approaching companies for financial or material aid, sterilizing equipment and using an internal wiki for accurate data storage. Although my specific focus during iGEM was protein purification, I taught myself adobe illustrator in order to generate higher quality designs for our {\href{http://2015.igem.org/Team:Freiburg}{\textcolor{blue}{\textit{website}}}}. At my current position, I took the initiative to further develop the facility's database (FileMaker)  --- leaving me with excellent organizational skills and able to improve data recording in any lab. I also attended a professional course on presenting with impact and project management for scientists and am able to apply these techniques to balance multiple projects at once while managing my time to keep ahead of deadlines. Finally, through a wide range of volunteering activities I have honed my interpersonal, organizational and communication skills, which will help in any situation whether organizing a lab or assisting in projects.\par\vspace*{2mm}

Working for Horizon as a research technician is a natural continuation of my experience, skills and passions and I believe I could make valuable contributions to Horizon's R\&D team. If you agree, I would appreciate the opportunity to discuss the position and my skills in more detail. Thank you for your consideration, I look forward to hearing from you and will be following up next week.

\end{spacing}
\vspace*{2mm} 
\makeletterclosing
\end{document}


%During my bachelor's thesis I gained insight into the cultivation of \textit{Nannochloropsis oceanica} and \textit{Phaeodactylum tricornutum} in the lab of Dr. Uwe Maier. For my master thesis I successfully cultivated and processed Synechocystis sp. PCC 6803 in the lab of Dr. Wolfgang Hess {\href{https://www.ncbi.nlm.nih.gov/pubmed/29517395}{\textcolor{blue}{{\textit{(Publication)}}}}}. These experiences have left me well equipped to prepare, cultivate and manipulate both algae and cyanobacteria and analyze their genetic background as well as their transcriptional activity and screen for secondary metabolites. The wide array of lectures and courses I took in plant sciences, translational biology and microbiology has left me with a solid foundation to genetically alter different organisms, analyze and translate genetic pathways like CRISPR-Cas systems and implement published methods. More generally, I have a proven ability to quickly learn and develop new procedures and protocols as when, during a reorganization of the lab, I was tasked with establishing protocols for the production of viral vector tools in mammalian cell culture using techniques that were new to both my supervisor and me. During this time I also began working in a BSL2 environment and am aware of the importance of stringently following safety guidelines and maintaining a clean working environment.
%Taking part in iGEM gave me the chance to work both independently and within an interdisciplinary team of 20 students and to present our team's findings to an international audience. iGEM also gave me a chance to hone my skills in organization and the daily maintenance of running a lab, including ensuring the availability of reagents, approaching companies and funding agencies for financial or material aid, cleaning and sterilizing equipment and using an internal wiki for accurate and reliable data storage. My specific focus during iGEM was protein purification but I also taught myself adobe illustrator in order to generate higher quality designs for our {\href{http://2015.igem.org/Team:Freiburg}{\textcolor{blue}{\textit{website}}}}. At my current position, I took the initiative to further develop and organize the facility's database (FileMaker) - leaving me with excellent organizational skills I could invest to improve data recording and storage in your lab. I have also attended a professional course on presenting with impact and project management for scientists and am able to apply these techniques to balance multiple projects at once while managing my time to keep ahead of deadlines. Finally, through a wide range of volunteering activities I have honed my interpersonal, organizational and communication skills which will help in any situation whether in the lab or presenting at conferences.\par%\vspace*{1mm}


%Given my skillset I believe I could make valuable contributions to the Demming-Adams and/or Adams lab and it would be an honor to contribute to your research. If you agree, I would appreciate the opportunity to discuss a potential position and my skills in more detail. Thank you for your time and consideration, I look forward to hearing from you.


 

\end{spacing}
%\vspace*{1mm} 
\makeletterclosing
\end{document}