\documentclass[11pt,a4paper,sans]{moderncv}

\usepackage{float}
\usepackage{caption}
\usepackage{fancyhdr}
\usepackage{setspace}
\usepackage{verbatim}
\usepackage[scale=0.8, top = 1.8cm, bottom = 3cm]{geometry}

\moderncvstyle{casual}                             
\moderncvcolor{blue}                               


%%%% FIX THIS SO IT LOOKS NICER
\fancypagestyle{titlepage}{
\fancyhead{}
\fancyfoot[CE, CO]{\textcolor{gray}{Via Ramarini 32, Monterotondo RM, 00015 \thinspace\thinspace $\bullet$ \thinspace\thinspace\mobilephonesymbol +39~(388)~059~1507 \thinspace\thinspace $\bullet$ \thinspace\thinspace \faSkype \thinspace\thinspace \href{skype:rabea.jesser}{rabea.jesser} \thinspace\thinspace \thinspace\thinspace \emailsymbol \href{mailto:rabeajesser@web.de}{rabeajesser@web.de} \thinspace\thinspace $\bullet$ \thinspace\thinspace \faLinkedin \thinspace\thinspace \href{https://www.linkedin.com/in/rabeajesser/}{https://www.linkedin.com/in/rabeajesser/}}}}


\name{\vspace{-5mm}Rabea Jesser}{\vspace{3mm}}

\begin{document}

%%%%%%%%%%%%%%%%%% RABEA NOTE %%%%%%%%%%%%%%%%%%%%%%


%%%%%%%%%%%%%%%%%%%RESEARCH FOCUS%%%%%%%%%%%%%
( i) developing larger and more sophisticated molecular toolkits for cyanobacteria and optimizing those tools to ensure high recombineering efficiencies,\\
ii) using genome-wide engineering techniques to identify genes which increase performance of cyanobacteria under stress conditions (salt, nutrient limitation, high/low light, etc) and\\
iii) designing production strains capable of using CO2 and sunlight to produce molecules of interest.\\



\thispagestyle{titlepage}
\recipient{Colorado School of Mines}{1500 Illinois St., Golden, CO 80401}
%%%% DONT FORGET TO UPDATE THIS OR USE \today
\date{\today}
%%%%% IF YOU KNOW WHO YOU'RE SENDING THIS TO THEN GIVE THEIR NAME
\opening{Dear Dr. Nanette Boyle,}
\closing{Sincerely,}
%\enclosure[Note]{Reference contacts and/or letters of reference will be sent upon request.}          
\makelettertitle
\begin{spacing}{1.1}
Just like yourself I am aware that humanity is in a big need of an alternative of a more sustainable source of energy and am convinced that photosynthetic organisms could play a key role in that. 
My hands-on experience with manipulating and analyzing algae and cyanobacteria, the strong work ethic and the team spirit I gained in the iGEM (international Genetically Engineered Machine) competition and the adaptive capacity I showed as a Technical Officer for Europe's flagship laboratory for the life sciences in Rome, make me a good addition to your laboratory. Furthermore, I work with precise attention to detail, am eager to learn and  am impassioned for the world of photosynthetic organisms.
\par%\vspace*{1mm}
%%%%%%EDITED TILL HERE
My theses {\href{https://www.ncbi.nlm.nih.gov/pubmed/29517395}{\textcolor{blue}{{\textit{(Publication)}}}}} have left me with excellent critical thinking skills and well-versed in gathering, analyzing, interpreting and communicating scientific data with meticulous attention to detail. 
More specifically, I have substantial experience in using PCR for molecular biology purposes and, with a proven ability to adapt to new topics and environments, I will have no issue familiarizing myself with flow cytometry assays. 
As an example, during a reorganization of my current lab, I consulted relevant literature to establish standard protocols for the production of viral vector tools in mammalian cell culture and their quantification via qPCR. 
Here, I precisely documented and monitored the generated data to identify areas for improvement and confered with my supervisor to continually improve the procedure. \par%\vspace*{0.5mm}
For the iGEM competition I participated in an interdisciplinary team of 20 highly motivated students.
Within a month we agreed on an influential topic, and after only eight months of wet lab we produced high-value  {\href{https://www.ncbi.nlm.nih.gov/pubmed/29803867}{\textcolor{blue}{\textit{data}}}}, finally presenting our team's findings on our {\href{http://2015.igem.org/Team:Freiburg}{\textcolor{blue}{\textit{website}}}} and at an international conference. 
This experience has not only left me with a strong work ethic, but also with the ability to efficiently identify the essentials from scientific findings and to present these in a comprehensive way to veterinarians or other clients. 
During this time we successfully ran our own lab independently, including ordering reagents, communicating with companies and funding agencies for financial or material aid, making and sterilizing media and keeping the lab and our data organized. \par 
At my current position our facility only consists of my supervisor and me, meaning I not only produce high-quality viral vectors and genetic constructs independently but also maintain a functional laboratory. 
Furthermore, I took the initiative to improve the facility's database (FileMaker)---leaving me with excellent organizational skills I can invest to ensure accurate data recording and storage at the Clinical Immunology Laboratory.  
I have also attended a professional course on presenting with impact and project management for scientists and am able to apply these techniques to balance multiple projects---currently more than 12 at once---while managing my time to deliver final products as quickly as possible.  
Additionally, as part of a {\href{https://adamascienza.com/summer-in-science/}{\textcolor{blue}{\textit{summer school}}}} for high school students I supervised and coordinated students alongside my daily schedule and am well prepared to supervise undergraduates or student hourly employees. \par%\vspace*{1mm}

Given my skill set, I believe I could make valuable contributions to the Avery lab and it would be an honor to contribute to the health and wellbeing of canine and feline patients. 
If you agree, I would appreciate the opportunity to discuss the position and my skills in more detail. 
Thank you for your time and consideration, I look forward to hearing from you soon.


 

\end{spacing}
%\vspace*{1mm} 
\makeletterclosing
\end{document}