\documentclass[11pt,a4paper,sans]{moderncv}

\usepackage{float}
\usepackage{caption}
\usepackage{fancyhdr}
\usepackage{setspace}
\usepackage{verbatim}
\usepackage[scale=0.8, top = 1.8cm, bottom = 3cm]{geometry}

\moderncvstyle{casual}                             
\moderncvcolor{blue}                               


%%%% FIX THIS SO IT LOOKS NICER
\fancypagestyle{titlepage}{
\fancyhead{}
\fancyfoot[CE, CO]{\textcolor{gray}{Via Ramarini 32, Monterotondo RM, 00015 \thinspace\thinspace $\bullet$ \thinspace\thinspace\mobilephonesymbol +39~(388)~059~1507 \thinspace\thinspace $\bullet$ \thinspace\thinspace \faSkype \thinspace\thinspace \href{skype:rabea.jesser}{rabea.jesser} \thinspace\thinspace \thinspace\thinspace \emailsymbol \href{mailto:rabeajesser@web.de}{rabeajesser@web.de} \thinspace\thinspace $\bullet$ \thinspace\thinspace \faLinkedin \thinspace\thinspace \href{https://www.linkedin.com/in/rabeajesser/}{https://www.linkedin.com/in/rabeajesser/}}}}


\name{\vspace{-5mm}Rabea Jesser}{\vspace{3mm}}

\begin{document}

%Job Summary
%GOT THAT:  BA/BS in science, education, or an environmental science-related field; MA/MS preferred
%DONT HAVE THAT: 1-2 years experience managing a gardening or growing program\\
%ONLY FROM VOLUNTAIRY ACTIVITY:1-2 years of outdoor or classroom teaching experience; knowledge of standards-based curriculum preferred\\
%GOT THAT: Strong work ethic and understanding that garden work is rewarding, but also physically demanding\\
%GOT THAT: Enjoy working outdoors in varying weather conditions\\
%GOT THAT:Ability to work with tools, basic woodworking skills preferred\\
%GOT THAT:Strong willingness and desire to learn\\
%GOT THAT: Excellent public speaking skills and willingness to teach a variety of audiences\\
%GOT THAT: Detail-oriented, organized, and able to provide exceptional customer service\\
%GOT THAT: Strong organizational skills\\
%GOT AT LEAST THE CREATIVE PART:D : Creative in curriculum design and development\\
%GOT THAT:Positive, flexible and friendly\\
%GOT THAT: Independently-driven team player\\
%GOT THAT: Valid driver's license and ability to drive 15-passanger vans\\
%GOT THAT: Ability to hike up to 4 miles on steep, uneven terrain carrying a pack up to 30 pounds\\
%GOT THAT: Knowledge and experience in using computers and software including Microsoft Office\\
%DONT HAVE THAT: Current Wilderness First Responder and CPR certifications preferred\\
%GOT THAT: Ability to work a full-time schedule with some evening or weekend responsibilities\\
%GOT THAT: Ability to speak Spanish preferred\\

%%%%%%%%%%%%% 			THOMAS NOTES 			%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\thispagestyle{titlepage}

\recipient{Walking Mountains Science Center}{318 Walking Mountains Lane\\Avon, CO 81620}
%%%% DONT FORGET TO UPDATE THIS OR USE \today
\date{\today}
%%%%% IF YOU KNOW WHO YOU'RE SENDING THIS TO THEN GIVE THEIR NAME
\opening{Dear Walking Mountains Science Center representative,}
\closing{Sincerely,}
%\enclosure[Note]{Publications, references and letters of recommendation can also be sent upon request.}          
\makelettertitle
\begin{spacing}{1.2}

Given my scientific background, a strong work ethic and deep interest in gardening, I would make an excellent Sowing Seeds Coordinator and relish the opportunity to help bring up the next generation of gardeners and environmental stewards. After a B.Sc. in Biology and participation in the iGEM (international Genetically Engineered Machine) competition, I received a M.Sc. in Biology before working with the European Molecular Biology Laboratory (EMBL) in Rome. Across various projects I have developed excellent public speaking skills, strong organizational skills with precise attention to details and have become an independently-driven team player able to provide exeptional customer service. Furthermore, I am a flexible and friendly person, enjoy working and hiking outdoors no matter how the weather is, am able to work with tools and do basic woodworking, have a proven ability to adapt to new challenges and am eager to learn.\par%\vspace*{1mm}

In a variety of volunteering activites I have had the opportunity to work with children of all ages. First I helped organizing a weekly daycare for elementary school kids while also teaching vaulting to kids from elementary to secondary school at a local horse farm. Later I was part of a team organizing a yearly summer trip for teenage girls, worked as a teamer at a language school in Malta for a couple of weeks and tutored at an international school in Malawi for a year. In Malawi I also organized a weekly youth group and a summer camp for teens. During my time at university I was part of a group trying to help international students settle in at German University and as part of the iGEM competition I co-organized a stall at the Freiburg Science Fair  where we tried to introduce children to molecular biology and extracted DNA from fruits. I truely enjoyed uniting my scientific background and my interests in teaching and would like to make this part of my daily work life.\\
During the iGEM competition, I became a self-motivated team-player able to efficiently cooperate with and communicate in an interdisciplinary team of 20 students. Throughout the competition I expanded my proficiency in Microsoft office suite, learned how to use an internal wiki for accurate data storage and taught myself adobe illustrator in order to generate higher quality designs for our {\href{http://2015.igem.org/Team:Freiburg}{\textcolor{blue}{\textit{website}}}}.\\
At my current position I expanded organizational skills valuable for the position of Sowing Seeds Coordinator - such as running projects independently, making sure all the necessary supplies are available or using and improving a database (FileMaker). Furthermore I showed I can quickly adapt to new challenges. For instance, during a reorganization of my current lab, I established procedures and SOPs that were new to both my supervisor and me. I also attended a professional course on presenting with impact and project management for scientists and am able to apply these techniques to balance multiple projects at once while managing my time to keep ahead of deadlines and to present to a variety of audiences. Coming from a scientific background  a full-time schedule with some evening or weekend responsibilities is not new to me. Alongside my own garden at home I helped setting up and running a community garden in the institute and a hiking \& climbing club and am aware that garden work is both rewarding and physically demanding.\par%\vspace*{1mm}

Aside from a scientific background, I bring a strong desire to learn, a fascination of nature and excellent interpersonal, organizational and communication skills shaped by a range of professional and volunteering challenges making me a perfect Sowing Seeds Coordinator. If you agree, I would appreciate the opportunity to discuss the position and my skills in more detail. Thank you for your time and consideration, I look forward to hearing from you and will follow up next week.


 

\end{spacing}
%\vspace*{1mm} 
\makeletterclosing
\end{document}
