\documentclass[11pt,a4paper,sans]{moderncv}

\usepackage{float}
\usepackage{caption}
\usepackage{fancyhdr}
\usepackage{setspace}
\usepackage{verbatim}
\usepackage[scale=0.8, top = 1.8cm, bottom = 3cm]{geometry}

\moderncvstyle{casual}                             
\moderncvcolor{blue}                               


%%%% FIX THIS SO IT LOOKS NICER
\fancypagestyle{titlepage}{
\fancyhead{}
\fancyfoot[CE, CO]{\textcolor{gray}{Via Ramarini 32, Monterotondo RM, 00015 \thinspace\thinspace $\bullet$ \thinspace\thinspace\mobilephonesymbol +39~(388)~059~1507 \thinspace\thinspace $\bullet$ \thinspace\thinspace \faSkype \thinspace\thinspace \href{skype:rabea.jesser}{rabea.jesser} \thinspace\thinspace \thinspace\thinspace \emailsymbol \href{mailto:rabeajesser@web.de}{rabeajesser@web.de} \thinspace\thinspace $\bullet$ \thinspace\thinspace \faLinkedin \thinspace\thinspace \href{https://www.linkedin.com/in/rabeajesser/}{https://www.linkedin.com/in/rabeajesser/}}}}


\name{\vspace{-5mm}Rabea Jesser}{\vspace{3mm}}

\begin{document}

%Job Summary

%cultivation of algae, Familiarity with algal cultivation methods and biofuel production processes is desirable. - got that covered, except for biofuel production but I don't think I have that
%fractionation of algal biomass to the main biochemical constituents - don't know if I have that
%the conversion of algal biomass components to fuels and chemicals - don't know if I have that
%analytical chemistry of a number of samples  - don't know if I have that
%keep notes and organize sample data, strong organizational background is needed, strong organizational skills are needed to set up a system for organization of large quantities of data. - got that covered
%keep up with the cultivation and physiological growth experiments in collaboration with researchers and technical staff - got that covered
%willingness to perform routine tasks to support research staff - got that covered
%Must have completed general organic chemistry, biology, molecular biology, and/or microbiology laboratory course - got that covered
%lecture courses in inorganic, analytical and organic chemistry. - got that covered
%strong background in chemistry or biochemistry is required - got that covered
%Experience with laboratory work is necessary  -got that covered
%instrument and chromatography experience is desired - don't think I have that
%experience with the Microsoft office suite, in particular Excel  - got that covered
%Strong communication skills including interpersonal, presentations, and writing required. Solid communication, interpersonal, project management and customer relations skills. Excellent communication skills. - got that covered
%Ability to work both independently and with a team is needed; Ability to independently conduct laboratory experiments,  - got that covered
%Proficient in research techniques and practices. - that should be obvious from where I worked, papers and that stuff
%stringently follow safety guidelines, Demonstrated ability to maintain a safe working environment. - got that covered
%report findings to mentor and/or supervisor. - got that covered


%%%%%%%%%%%%% 			THOMAS NOTES 			%%%%%%%%%%%%%%%%%%%%%%%
% Just wanted to say, w.r.t. the above: If they are saying stuff that you don't have, try to highlight experiences
% where you were able to learn new techniques quickly. So they should be thinking: ``She's got most everything 
% we need and she is definitely smart enough to figure the rest out
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\thispagestyle{titlepage}

\recipient{National Bioenergy Center}{National Renewable Energy Laboratory\\15013 Denver West Parkway, Golden, CO 80401}
%%%% DONT FORGET TO UPDATE THIS OR USE \today
\date{\today}
%%%%% IF YOU KNOW WHO YOU'RE SENDING THIS TO THEN GIVE THEIR NAME
\opening{Dear NREL Representative,}
\closing{Sincerely,}
\enclosure[Note]{M.Sc. Thesis, B.Sc., references and a more complete CV can also be sent upon request.}          
\makelettertitle
\begin{spacing}{1.15}

Having seen the destructive consequences of our overreliance on fossil fuels, I have an abiding desire to contribute towards the development of alternative fuels that would allow our society to prosper without detriment to the planet. NREL's National Bioenergy Center, with its dedication to finding sustainable, secure transportation systems, represents the perfect fit for my ambitions and passions. Likewise, having focused on organisms that could be used for the generation of biofuels or secondary metabolites, I believe my skills and background make me an excellent candidate for NREL.\par\vspace*{1mm}

During my bachelor thesis I gained insight into the cultivation of \textit{Nannochloropsis oceanica} and \textit{Phaeodactylum tricornutum} and during my master thesis I successfully cultivated and processed Synechocystis sp. PCC 6803 {\href{https://www.ncbi.nlm.nih.gov/pubmed/29517395}{\textcolor{blue}{{\textit{(Publication)}}}}}. These experiences have left me well prepared to work preparing and cultivating both algae and cyanobacteria. The wide array of lectures and courses I took in biochemistry, organic chemistry, molecular biology and microbiology has also left me with a solid foundation to learn and develop new procedures and protocols in the lab.\par\vspace*{1mm}

As part of a student competition called iGEM (international Genetically Engineered Machine), I learned how to work independently and cooperate with an interdisciplinary team of 20 students. To improve team coordination and communication I expanded my proficiency in handling Microsoft office suite and gene analysis softwares (Geneious, Snapgene) and learned how to set up and organize databases (FileMaker) and use an internal wiki for accurate and reliable data storage. Through iGEM and my theses I learned to clearly communicate results to my team and a wider audience using oral presentations and a {\href{http://2015.igem.org/Team:Freiburg}{\textcolor{blue}{\textit{website}}}}. To further hone this skill I attended a professional course on proper presentation.\par\vspace*{1mm}

My current team at the European Molecular Biology Laboratory (EMBL) comprises two members, giving me ample experience in the basic organization and daily maintenance of running a lab. During my time here I have acquired a broad range of responsibilities and have learned to balance multiple projects while managing my time to keep ahead of deadlines. Within the first few months at EMBL my job description changed quite dramatically and I had to quickly learn techniques that were new to both my supervisor and me. Due to the reshaping I also started working in a BSL2 environment and am thus aware of the importance of stringently following safety guidelines and maintaining a safe working environment.\par\vspace*{1mm}

Besides the experience I collected in different laboratory environments over time, I bring excellent interpersonal, organizational and communication skills shaped by a range of volunteering activities. Given my skillset I believe I could make valuable contributions to NBC's team and it would be an honor to contribute to your research into algal biofuels. If you agree, I would appreciate the opportunity to discuss the position and my potential contributions in more detail. Thank you for your time and consideration, I look forward to hearing from you.


 

\end{spacing}
%\vspace*{1mm} 
\makeletterclosing
\end{document}
