\documentclass[11pt,a4paper,sans]{moderncv}

\usepackage{float}
\usepackage{caption}
\usepackage{fancyhdr}
\usepackage{setspace}
\usepackage{verbatim}
\usepackage[scale=0.8, top = 1.6cm, bottom = 2cm]{geometry}

\moderncvstyle{casual}                             
\moderncvcolor{blue}                               


%%%% FIX THIS SO IT LOOKS NICER
\fancypagestyle{titlepage}{
\fancyhead{}
\fancyfoot[CE, CO]{\textcolor{gray}{Via Ramarini 32, Monterotondo RM, 00015 \thinspace\thinspace $\bullet$ \thinspace\thinspace\mobilephonesymbol +39~(388)~059~1507 \thinspace\thinspace $\bullet$ \thinspace\thinspace \faSkype \thinspace\thinspace \href{skype:rabea.jesser}{rabea.jesser} \thinspace\thinspace \thinspace\thinspace \emailsymbol \href{mailto:rabeajesser@web.de}{rabeajesser@web.de} \thinspace\thinspace $\bullet$ \thinspace\thinspace \faLinkedin \thinspace\thinspace \href{https://www.linkedin.com/in/rabeajesser/}{https://www.linkedin.com/in/rabeajesser/}}}}


\name{\vspace{-5mm}Rabea Jesser}{\vspace{3mm}}

\begin{document}

%GEVO Fermentation Research Scientist
%support activities within the FERMENTATION and PROCESS DEVELOPMENT areas\\
%GENERAL LAB DUTIES: prepare MEDIA, maintain SUPPLY stocks, Equipment and glassware cleaning, assembly and sterilization of laboratory equipment, Medium preparation, filtration and/or in situ sterilization\\
%EDUCATION: A Masters level degree in microbiology or biological sciences\\
%SKILLS: Demonstrated mechanical ability to maintain, troubleshoot, and repair laboratory equipment;  set up, operate, clean and maintain fermentation and recovery EQUIPMENT at the bench and pilot plant scale, OPERATE bench and pilot plant fermentation and/or shake flask and supporting equipment systems\\
%SKILLS: Attention to detail. \\
%SKILLS: Ability to develop, set up, execute, and interpret experimental data, collect and record EXPERIMENT SAMPLES, perform sample ASSAYS (YSI sugar measurements, micropipetting, dilutions, cell counts, sample preparation for GC, LC, or IC, accurate volumetric and gravimetric measurements, perform DATA ANALYSIS and REPORTING, Accurately and precisely preparing and analyzing samples in complex matrices, filtration and/or in situ sterilization\\
%SKILLS: designing, performing, and analyzing data from fermentations at the bench scale in shake flasks or fermenters, provide FEEDBACK and IMPROVE experiment and sampling protocols while using\\
%identify errors or areas for IMPROVEMENT, provide RECOMMENDATIONS and follow through tasks to completion.\\
%QUALITY: quality statistical analysis of experimental results and routinely monitoring accuracy and precision of data collected\\
%Write, improve, and maintain Standard Operation Procedures\\
%PRESCISE DOCUMENTATION: maintaining accurate and thorough lab notebook and electronic documentation; technical reports to communicate results within team and across departments\\
%SKILLS: aseptic technique, operation of bench fermenters, use of laminar flow hoods, use of autoclaves, serial dilutions, streak Plates, membrane filter plating, light microscopy, cell counting by hemocytometer, gram staining, and cell culture maintenance
%SKILLS: Demonstrated ability to quickly learn, apply new concepts and techniques, and perform quality control of data generated\\
%SKILLS: The candidate for this position must be a CLEAR COMMUNICATOR, able to WORK AND THINK INDEPENDENTLY, be a TEAM PLAYER and willing to WORK OVERTIME on occasion\\
%FLEXIBLE work hours (work morning or evening hours and an occasional weekend as required) and TRAVEL (10 percent time annually, at a commercial plant location outside of Colorado) are required for this position, work shifts with evening hours as experiments dictate\\
%Excellent WRITTEN AND VERBAL COMMUNICATION and INTERPERSONAL skills (Respects fellow teammates and works well across teams to accomplish team goals) are required. prepare and deliver information in a concise, accurate and professionally written format\\
%INTERDISCIPLINARY TEAM: Collaborate with Analytical Chemists\\
%Microsoft Office products (proficiency with Excel in particular), Data Acquisition/Data Analysis Software and/or with DATABASE!!! software\\

%%%%%%%low carbon, low environmental footprint fuels and chemicals reduce their dependence on petroleum and to improve the sustainability of the chemical business system isobutanol produced from yeast + product recovery system


%%%%%%%%%%%%% 			THOMAS NOTES 			%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\thispagestyle{titlepage}

\recipient{Gevo, Inc.}{345 Inverness Drive South\\Englewood, CO 80112 \vspace{-2mm}}
%%%% DONT FORGET TO UPDATE THIS OR USE \today
\date{\today}
%%%%% IF YOU KNOW WHO YOU'RE SENDING THIS TO THEN GIVE THEIR NAME
\opening{Dear Gevo Inc. representative,\vspace{-2mm}}
\closing{Sincerely,\vspace*{-4mm} }
%\enclosure[Note]{Reference contacts and/or letters of reference will be sent upon request.}          
\makelettertitle
\begin{spacing}{1.15}

Given my strong scientific background and deep interest in the generation of biofuels, I would make an excellent Fermentation Research Scientist and relish the opportunity to help advance low carbon, low environmental footprint fuels, chemicals and feedstock. After a B.Sc. in Biology and participation in the iGEM (international Genetically Engineered Machine) competition, I received a M.Sc. in Biology before working with the European Molecular Biology Laboratory (EMBL) in Rome. Across various research projects I have worked both independently and as part of a team, gaining strong problem-solving skills, precise attention to detail and excellent communication and interpersonal skills. Furthermore, I have a proven ability to quickly adapt to new challenges, apply new techniques, provide quality controlled data and am able to use, maintain and troubleshoot laboratory equipment.\par\vspace*{2mm}

During my B.Sc. thesis I worked with \textit{Nannochloropsis oceanica} and \textit{Phaeodactylum tricornutum} while for my M.Sc. thesis I cultivated Synechocystis sp. PCC 6803 {\href{https://www.ncbi.nlm.nih.gov/pubmed/29517395}{\textcolor{blue}{{\textit{(Publication)}}}}}. Through these experiences I developed excellent analytical and critical thinking skills and became well-versed in gathering, analyzing, recording and quality checking scientific data with precise attention to detail. The wide array of lectures and courses I took in microbiology and translational biology has introduced me to basic molecular biology techniques like gram staining or light microscopy and left me with a solid foundation to collect, analyze and interpret experimental data based on available literature. More generally, I have consistently shown I can quickly learn new procedures and protocols. For instance, during a reorganization of my current lab, I consulted a variety of available protocols and methods to establish SOPs and the necessary quality control for the production and quantification of viral vector tools in mammalian cell culture. In this process I identified areas of improvement by monitoring the quality of generated data, constantly provided feedback and recommendations for improvement to my supervisor and implemented resulting changes. During this time I improved my aseptic technique, became more familiar with using laminar flow hoods and diffferent cell counting methods, and began working in a BSL2 environment - making me aware of the importance of stringently following safety guidelines to maintain a clean, safe and efficient working environment. In the genetic engineering part of my current position I collected further experience in micropipetting, streaking cells for single colonies and preparing serial dilutions. \par\vspace*{2mm}
 
During iGEM I worked within an interdisciplinary team of 20 students preparing me to collaborate with Gevo's Analytical Chemists and to flourish in team environments while accomplishing common goals together. This experience has left me ready to accurately record, prepare and communicate findings or suggestions concisely, comprehensively and professionally within the team and across departments. iGEM also provided an opportunity to hone my skills in the daily upkeep of a lab, including ensuring the availability of supply stocks and the functionality of laboratory equipment as well as preparation of media using accurate volumentric and gravimetric measurements and cleaning and sterilizing glassware or other equipment using autoclaves or filter sterilization. At my current position, I took the initiative to increase my proficiency in Microsoft Office products, particularly Excel for data analysis and taught myself how to use and improve the facility's database (FileMaker) to precisely maintain electronic documentation alongside the lab notebook. I also attended a professional course on presenting with impact and project management for scientists and am able to apply these techniques to balance multiple projects at once while managing my time to keep ahead of deadlines. Finally, I am used to flexible work hours and am willing to travel as required.\par\vspace*{2mm}

Working for Gevo, Inc. as a Fermentation Research Scientist is a natural continuation of my experience, skills and passions and I believe I could make valuable contributions to lead the change to low carbon fuels and chemicals. If you agree, I would appreciate the opportunity to discuss the position and my skills in more detail. Thank you for your consideration, I look forward to hearing from you and will be following up next week.

\end{spacing}
\vspace*{2mm} 
\makeletterclosing
\end{document}


%During my bachelor's thesis I gained insight into the cultivation of \textit{Nannochloropsis oceanica} and \textit{Phaeodactylum tricornutum} in the lab of Dr. Uwe Maier. For my master thesis I successfully cultivated and processed Synechocystis sp. PCC 6803 in the lab of Dr. Wolfgang Hess {\href{https://www.ncbi.nlm.nih.gov/pubmed/29517395}{\textcolor{blue}{{\textit{(Publication)}}}}}. These experiences have left me well equipped to prepare, cultivate and manipulate both algae and cyanobacteria and analyze their genetic background as well as their transcriptional activity and screen for secondary metabolites. The wide array of lectures and courses I took in plant sciences, translational biology and microbiology has left me with a solid foundation to genetically alter different organisms, analyze and translate genetic pathways like CRISPR-Cas systems and implement published methods. More generally, I have a proven ability to quickly learn and develop new procedures and protocols as when, during a reorganization of the lab, I was tasked with establishing protocols for the production of viral vector tools in mammalian cell culture using techniques that were new to both my supervisor and me. During this time I also began working in a BSL2 environment and am aware of the importance of stringently following safety guidelines and maintaining a clean working environment.
%Taking part in iGEM gave me the chance to work both independently and within an interdisciplinary team of 20 students and to present our team's findings to an international audience. iGEM also gave me a chance to hone my skills in organization and the daily maintenance of running a lab, including ensuring the availability of reagents, approaching companies and funding agencies for financial or material aid, cleaning and sterilizing equipment and using an internal wiki for accurate and reliable data storage. My specific focus during iGEM was protein purification but I also taught myself adobe illustrator in order to generate higher quality designs for our {\href{http://2015.igem.org/Team:Freiburg}{\textcolor{blue}{\textit{website}}}}. At my current position, I took the initiative to further develop and organize the facility's database (FileMaker) - leaving me with excellent organizational skills I could invest to improve data recording and storage in your lab. I have also attended a professional course on presenting with impact and project management for scientists and am able to apply these techniques to balance multiple projects at once while managing my time to keep ahead of deadlines. Finally, through a wide range of volunteering activities I have honed my interpersonal, organizational and communication skills which will help in any situation whether in the lab or presenting at conferences.\par%\vspace*{1mm}


%Given my skillset I believe I could make valuable contributions to the Demming-Adams and/or Adams lab and it would be an honor to contribute to your research. If you agree, I would appreciate the opportunity to discuss a potential position and my skills in more detail. Thank you for your time and consideration, I look forward to hearing from you.


 

\end{spacing}
%\vspace*{1mm} 
\makeletterclosing
\end{document}