\documentclass[11pt,a4paper,sans]{moderncv}

\usepackage{float}
\usepackage{caption}
\usepackage{fancyhdr}
\usepackage{setspace}
\usepackage{verbatim}
\usepackage[scale=0.8, top = 1.8cm, bottom = 3cm]{geometry}

\moderncvstyle{casual}                             
\moderncvcolor{blue}                               


%%%% FIX THIS SO IT LOOKS NICER
\fancypagestyle{titlepage}{
\fancyhead{}
\fancyfoot[CE, CO]{\textcolor{gray}{Via Ramarini 32, Monterotondo RM, 00015 \thinspace\thinspace $\bullet$ \thinspace\thinspace\mobilephonesymbol +39~(388)~059~1507 \thinspace\thinspace $\bullet$ \thinspace\thinspace \faSkype \thinspace\thinspace \href{skype:rabea.jesser}{rabea.jesser} \thinspace\thinspace \thinspace\thinspace \emailsymbol \href{mailto:rabeajesser@web.de}{rabeajesser@web.de} \thinspace\thinspace $\bullet$ \thinspace\thinspace \faLinkedin \thinspace\thinspace \href{https://www.linkedin.com/in/rabeajesser/}{https://www.linkedin.com/in/rabeajesser/}}}}


\name{\vspace{-5mm}Rabea Jesser}{\vspace{3mm}}

\begin{document}

%!!!!!!!!!!!!!!!!!!DEADLINE:  08/05/2018 5.8.18!!!!!!!!!!!!!!!!!!
%technician for diagnostic molecular biology and immunology for companion animals (canine and feline) \\

%meticulous attention to detail\\
%a strong work ethic \\
%the ability to communicate well with clients. \\
%result: gain substantial experience with PCR and flow cytometry assays.\\
%BS in Microbiology or related field and at least 1 year of previous experience in the laboratory\\
%Excellent communication skills\\
%Veterinary experience is preferred but not required. \\
%Some experience with cellular and molecular assays is desirable.\\
%Duties:
%Carrying out PCR and flow cytometry assays on clinical samples from small animal patients for the Clinical Immunology Service. Performing flow cytometry and PARR assays, interpreting data\\
%Carrying out client communications (veterinarians are our main clients), entering sample data, reporting and other administrative responsibilities associated with the Service.\\
%Maintaining the laboratory, including ordering, making media, refilling liquid nitrogen, keeping order and other responsibilities to keep the lab running smoothly.\\
%Supervising undergraduate and student hourly employees as needed.\\
%\textbf{Apply with}: 
%cover letter with qualifications\\
%curriculum vitae,\\
%name and contact information for three professional references.\\


\thispagestyle{titlepage}
\recipient{Clinical Immunology Laboratory }{Colorado State University, Avery Lab \\Fort Collins CO 80523-1619}
%%%% DONT FORGET TO UPDATE THIS OR USE \today
\date{\today}
%%%%% IF YOU KNOW WHO YOU'RE SENDING THIS TO THEN GIVE THEIR NAME
\opening{Dear Dr. Avery,}
\closing{Sincerely,}
%\enclosure[Note]{Reference contacts and/or letters of reference will be sent upon request.}          
\makelettertitle
\begin{spacing}{1.2}

Given my laboratory experience, a strong work ethic and prescise attention to detail in my work, I would make an excellent technician for the Avery lab and relish the opportunity to help diagnosing companion animals around the US and the world. After a B.Sc. in Biology and participation in the iGEM (international Genetically Engineered Machine) competition, I received a M.Sc. in Biology before continuing on to work with Europe's flagship laboratory for the life sciences, EMBL, in Rome. Across various research projects I have worked both independently and as part of a team, gaining strong problem-solving skills, precise attention to detail and excellent communication skills. Furthermore, I have a proven ability to quickly adapt to new challenges, maintain and troubleshoot laboratory equipment and provide high quality data.
\par%\vspace*{1mm}

My theses {\href{https://www.ncbi.nlm.nih.gov/pubmed/29517395}{\textcolor{blue}{{\textit{(Publication)}}}}} have left me with excellent critical thinking skills and well-versed in gathering, analyzing, interpreting and communicating scientific data with precise attention to detail. More specific, I have substantial experience in using PCR for molecular biology purposes and since I adept well to new topics and environments I can quickly become familiar with flow cytrometry assays. For instance, during a reorganization of my current lab, I consulted relevant literature to establish standard protocols for the production and for a qPCR based approach for quantification of viral vector tools in mammalian cell culture. Here I monitored data to identify areas for improvement and confered with my supervisor to improve the procedure. \par%\vspace*{0.5mm}
Taking part in iGEM gave me the chance to work both independently and within an interdisciplinary team of 20 highly motivated students and to present our team's findings to an international audience at a conference to fellow scientists and at a local science fair to the general public. During this time I also taught myself adobe illustrator in order to generate higher quality designs for our {\href{http://2015.igem.org/Team:Freiburg}{\textcolor{blue}{\textit{website}}}}, meaning I can efficiently identify the essentials from scientific findings and present them in a comprehensive way to veterinarians or other clients. iGEM also gave me a chance to hone my skills in organization and the daily maintenance of running a lab, including ordering reagents, communicating with companies and funding agencies for financial or material aid, making and sterilizing media and keeping the lab orderly. \par 
At my current position, I futher developed my skills in maintaining a laboratory and took the initiative to improve the facility's database (FileMaker) - leaving me with excellent organizational skills I will invest to run your lab smoothly and ensure accurate data recording and storage. I have also attended a professional course on presenting with impact and project management for scientists and am able to apply these techniques to balance multiple projects at once while managing my time to keep ahead of deadlines. Additionally, I showed my ablity to supervise and coordinate students alongside my daily schedule by tutoring a high school student during a yearly summer in science program at my current position. Finally, through a wide range of volunteering activities I have honed my interpersonal, organizational and communication skills which will help in any situation whether in the carrying our client communications or other administrative responsibilities.\par%\vspace*{1mm}


Given my skillset I believe I could make valuable contributions to the Avery lab and it would be an honor to contribute to the accurate diagnosis of canine and feline patients. If you agree, I would appreciate the opportunity to discuss a the position and my skills in more detail. Thank you for your time and consideration, I look forward to hearing from you soon.


 

\end{spacing}
%\vspace*{1mm} 
\makeletterclosing
\end{document}
