%%%%%%%%%%%%%%%%%   HOW TO COMMENT!!! %%%%%%%%%%%%%%%%%%%%%%%
% Begin all comments particular to this document with `Thomas:' (unless it appears in `THOMAS GENERAL NOTES SECTION')
%To answer comments  please INDENT (just hit tab once or twice) and start with `Rabea:' 
%

%%%%%%%%%%%%%%%%%%%%%%%%% 		CHECKLIST		%%%%%%%%%%%%%%%%%%%%%%%%%
%
% 		Did you:
%				1) Check for the correct date?
%				2) Check that the recipeient's name and address were correct?
%				3) Copy into Word for spelling errors?
%				4) Use a word counter online to check for overused language?


%%%%%%%%%%%%%%%%%%%%%		 DOCUMENT CLASS, PACKAGES 		%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[11pt,a4paper,sans]{moderncv}

\usepackage{float, caption, fancyhdr, setspace, verbatim, xcolor}
\usepackage[normalem]{ulem} % Added this for strikeouts
\usepackage[scale=0.8, top = 3cm, bottom = 3cm]{geometry}                  


%%%%%%%%%%%%%%%%%%%%%%%%%%% 		FOOTER, HEADER, MODERNCV INPUTS		 %%%%%%%%%%%%%%%%%%%%%%%%%%%
\fancypagestyle{titlepage}{
\fancyhead{}
\fancyfoot[CE, CO]{\textcolor{gray}{Via Ramarini 32, Monterotondo RM, 00015 \thinspace\thinspace $\bullet$ \thinspace\thinspace\mobilephonesymbol +39~(388)~059~1507 \thinspace\thinspace $\bullet$ \thinspace\thinspace \faSkype \thinspace\thinspace \href{skype:rabea.jesser}{rabea.jesser} \thinspace\thinspace \thinspace\thinspace \emailsymbol \href{mailto:rabeajesser@web.de}{rabeajesser@web.de} \thinspace\thinspace $\bullet$ \thinspace\thinspace \faLinkedin \thinspace\thinspace \href{https://www.linkedin.com/in/rabeajesser/}{https://www.linkedin.com/in/rabeajesser/}}}}
\name{\vspace{-5mm}Rabea Jesser}{\vspace{3mm}}
\moderncvstyle{casual}                             
\moderncvcolor{blue}
\thispagestyle{titlepage}
% DONT FORGET TO UPDATE THIS!
\recipient{The Land Institute}{ 2440 E Water Well Rd,\\ Salina, Kansas 67401}
% DONT FORGET TO UPDATE THIS OR USE \today
\date{\today}
%%%%% IF YOU KNOW WHO YOU'RE SENDING THIS TO THEN GIVE THEIR NAME
\opening{Dear Land Institute Representative,\vspace{-2mm}}
\closing{Sincerely,}
%\enclosure[Note]{M.Sc. Thesis, B.Sc., references and a more complete CV can also be sent upon request.}   


%%%%%%%%%%%%%%%%%%%% NOTES FOR CONTEXT OF LETTER, INFO ON ADDRESSEE 

%Mission Statement:
%When PEOPLE, LAND, and COMMUNITY are as ONE, all three members prosper; when they relate not as MEMBERS but as competing interests, all three are exploited. By consulting NATURE as the SOURCE AND MEASURE of that membership, The Land Institute seeks to develop an agriculture that will SAVE SOIL from being lost or poisoned, while promoting a COMMUNITY LIFE at once prosperous and enduring.
%mimic nature throught policultures\\
%50 year farm bill\\
%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% 

%%%%%%%%%%%%%%%% 			THOMAS GENERAL NOTES 			%%%%%%%%%%%%%%%%%%%%%%%%%%
 scientist, the accountant who converses with nature, a true artist devoted to the building of agriculture and culture to match the scenery presented to those first European eyes


%%%%%%%%%%%%%%%%%%%%%		BEGIN DOCUMENT		%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}     
\makelettertitle
\begin{spacing}{1.2}

Currently the best part of my working day is going outside and getting my hands dirty in our little community garden at the institute. After my boyfriend drew my attention to the Land Instutute I can not stop thinking how great it would be to become one of the scientists that Wes Jackson envisoned---to converse with nature to revolutionize mordern argriculture. 
My research experience combined with the team spirit and interpersonal skills I developed during the iGEM (international Genetically Engineered Machine) competition make me a perfect fit for the Land Institute. 
Furthermore, the initiative and ability to adapt to new situations I have displayed while working at Europe's flagship laboratory for the life sciences (EMBL) ensure that I can quickly transition to your lab.\par\vspace*{3mm}


My journey with photosynthetic organisms started during my B.Sc. thesis with the diatom \textit{P. tricornutum}, in which I expressed a recombinant antibody to characterize intracellular protein transport. 
Later during my M.Sc. thesis, I explored the use of the endogenous CRISPR-Cas system of Synechocystis sp. PCC6803 in metabolic engineering by modifying the Cas proteins of one of its CRISPR loci via homologous recombination and providing an artificial crRNA via conjugation.
		%Rabea: maybe this should move up:
In the process I became familiar with extracting and analyzing RNA \textit{in vitro} and from Synechocystis cultures, documenting pigment content via photometric measurements and producing genetic constructs and recombinant proteins in \textit{E. coli}.
		%Rabea: I didn't like this sentence, how about this:
Having learned from previous default, I  {\href{https://www.tandfonline.com/eprint/vmAQ3vjYGdZIZpIKQTIT/full}{\textcolor{blue}{{\textit{published}}}}} the findings of my M.Sc. thesis.
		%Rabea: and I didn't publish on the metabolic engineering because it didn't work the way we had it designed, in the end I only published further characterization of the Cas6 protein, not to say that's worth nothing but I cannot write it the way it was
\par\vspace*{3mm}
 
During this time I also participated in an interdisciplinary team of 20 students to develop a low-cost, multiplexed and label-free diagnostic tool as part of the Univerisity of Freiburg's team in the iGEM competition.
Within eight months of wet lab we produced high-value {\href{https://www.ncbi.nlm.nih.gov/pubmed/29803867}{\textcolor{blue}{\textit{data}}}}, presenting our findings on our {http://2015.igem.org/Team:Freiburg/Home_Intro}{\textcolor{blue}{\textit{website}}}} and at iGEM's international conference at MIT, where we were awarded a Gold medal and nominated for Best Health and Medicine Project, Best Innovation in Medicine and Best Wiki.
Throughout iGEM we successfully ran our own lab independently, including ordering reagents, communicating with companies and funding agencies for financial or material aid, making and sterilizing media and keeping the lab and our data organized. 
This experience further demonstrates my strong work ethic, team-player attitude and ability to distill the essentials from scientific findings for my team and a wider audience.\par\vspace*{3mm}
		
After my M.Sc., I began working in EMBL's Genetic Engineering Facility, which evolved into the Genetic and Viral Engineering Facility soon after I started. 
As part of this transition, I quickly adapted and established new protocols for the production and quantification of viral vector tools in mammalian cell culture. 			
Initially our two person team only provided recombinant AAV, but as my skills progressed, the scope of my portfolio has expanded to include recombinant Lentivirus and we are in the process of adding HSV.
In my position with EMBL I have expanded on my organizational skills and taken the initiative to extend the facility's database and automate calculations for protocols using Excel and Filemaker, helping streamline the lab and more consistently produce and record valuable data.
Additionally, I am continually applying techniques I learned from a professional development course on project management for scientists across more than 12 projects to deliver high quality final products in a timely fashion to our partners.\par\vspace*{3mm}

Although EMBL offered extensive experience in the lab and provided room for growth, the research focus is simply not after my own heart.
Your institute offers the opportunity both to continue my journey with photosynthetic organisms and help reunite people, land and the community.
If you agree, I would appreciate the opportunity to discuss any potential position and my contributions in more detail. 
Thank you for your time and consideration, I look forward to hearing from you.
 
\vspace{5mm}
\end{spacing}
\makeletterclosing
\end{document}