\documentclass[11pt,a4paper,sans]{moderncv}

\usepackage{float}
\usepackage{caption}
\usepackage{fancyhdr}
\usepackage{setspace}
\usepackage{verbatim}
\usepackage[scale=0.8, top = 1.8cm, bottom = 3cm]{geometry}

\moderncvstyle{casual}                             
\moderncvcolor{blue}                               


%%%% FIX THIS SO IT LOOKS NICER
\fancypagestyle{titlepage}{
\fancyhead{}
\fancyfoot[CE, CO]{\textcolor{gray}{Via Ramarini 32, Monterotondo RM, 00015 \thinspace\thinspace $\bullet$ \thinspace\thinspace\mobilephonesymbol +39~(388)~059~1507 \thinspace\thinspace $\bullet$ \thinspace\thinspace \faSkype \thinspace\thinspace \href{skype:rabea.jesser}{rabea.jesser} \thinspace\thinspace \thinspace\thinspace \emailsymbol \href{mailto:rabeajesser@web.de}{rabeajesser@web.de} \thinspace\thinspace $\bullet$ \thinspace\thinspace \faLinkedin \thinspace\thinspace \href{https://www.linkedin.com/in/rabeajesser/}{https://www.linkedin.com/in/rabeajesser/}}}}


\name{\vspace{-5mm}Rabea Jesser}{\vspace{3mm}}

\begin{document}
%Breaking down lignose - Gregg Beckham\\
%depolymerize lignin in an integrated biorefinery context and subsequently upgrade lignin-derived aromatics into value-added chemicals to realize a more holistic, integrated approach to biomass conversion\\
%biological upgrading of sugars\\
%bench-scale catalytic and separations processes \\
%enzymatic processes for both deconstructing cellulose and also assembling it \\
%use of novel metabolic enzymes for biologically producing fuel precursors\\
%begin a working group to figure out ways to incorporate concepts of the Circular Materials Economy into the designs of everything from coffee mug lids to wind turbines, cutting down on waste generated by today’s linear economy model. \\



%%%%%%%%%%%%% 			THOMAS NOTES 			%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\thispagestyle{titlepage}

\recipient{National Bioenergy Center}{National Renewable Energy Laboratory\\15013 Denver West Parkway, Golden, CO 80401}
%%%% DONT FORGET TO UPDATE THIS OR USE \today
\date{\today}
%%%%% IF YOU KNOW WHO YOU'RE SENDING THIS TO THEN GIVE THEIR NAME
\opening{Dear Dr.  Beckham,}
\closing{Sincerely,}
%\enclosure[Note]{M.Sc. Thesis, B.Sc., references and a more complete CV can also be sent upon request.}          
\makelettertitle
\begin{spacing}{1.15}

%Just like yourself I don't wish to see the natural world being degraded beyond repair and am fed up with being a contributor or at least a bystander in this destruction. 
%It is my abiding desire to be part of the solution and contribute to your efforts in providing a holistic, integrated approach to biomass conversion and in finding ways to integrate concepts of Circular Materials Economy into the designs of everything. 
%With my hands-on experience with manipulating and analyzing different microorganisms, the strong work ethic and the team spirit I gained in the iGEM (international Genetically Engineered Machine) competition and the adaptive capacity I showed as a Technical Officer for Europe's flagship laboratory for the life sciences in Rome, I bring the neccessary background knowledge and the enthusiasm and eagerness to learn to make up for any deficiency.\par\vspace*{1mm}

Sharing NREL's passion for renewables, I will wholeheartedly invest my laboratory experience, strong work ethic and analytical thinking to find new biocatalysts and unravel their functionality.
My experience in engineering and analyzing microorganisms like algae, cyanobacteria and \textit{E. coli} combined with the team spirit and interpersonal skills I developed during the iGEM (international Genetically Engineered Machine) competition make me an excellent fit for your group. 
Furthermore, the initiative and ability to adapt to new situations I have displayed while working at Europe's flagship laboratory for the life sciences (EMBL) ensure that I can quickly transition to your lab and begin making contributions from day one.\par\vspace*{3mm}

I always had a special interest in applying molecular biology for the good of the environment, so for my B.Sc. thesis I wanted to explore the biotechnological potential of diatoms. 
Later during my M.Sc. thesis, I analyzed using the endogenous CRISPR-Cas system of Synechocystis sp. PCC6803 in metabolic engineering and thereby further characterized the Synechocystis crRNA maturation endonuclease Cas6-1
{\href{https://www.tandfonline.com/eprint/vmAQ3vjYGdZIZpIKQTIT/full}{\textcolor{blue}{{\textit{Publication}}}}}.
In the process I became familiar with extracting and analyzing RNA \textit{in vitro} and from Synechocystis cultures, documenting pigment content via photometric measurements and producing genetic constructs and recombinant proteins in \textit{E. coli}.
\par\vspace*{3mm}
 
During this time I also participated in an interdisciplinary team of 20 students to develop a low-cost, multiplexed and label-free diagnostic tool as part of the Univerisity of Freiburg's team in the iGEM competition.
Within eight months of wet lab we produced high-value {\href{https://www.ncbi.nlm.nih.gov/pubmed/29803867}{\textcolor{blue}{\textit{data}}}}, presenting our findings on our {\href{http://2015.igem.org/Team:Freiburg/Home_Intro}{\textcolor{blue}{\textit{website}}}} and at iGEM's international conference at MIT, where we were awarded a Gold medal and nominated for Best Health and Medicine Project, Best Innovation in Medicine and Best Wiki.
Throughout iGEM we successfully ran our own lab independently, including ordering reagents, communicating with companies and funding agencies for financial or material aid, making and sterilizing media and keeping the lab and our data organized.\par\vspace*{3mm}
		
After my M.Sc., I began working in EMBL's Genetic Engineering Facility, which evolved into the Genetic and Viral Engineering Facility soon after I started. 
I quickly adapted and engaged myself in implementing new protocols for the production and quantification of viral vector tools in mammalian cell culture  in addition to producing a number of genetic constructs via recombineering and other cloning strategies.
Initially our two person team only provided recombinant AAV, however, as my skills progressed, our portfolio has expanded to include recombinant lentivirus and we are in the process of adding HSV.
I have also taken the initiative to extend the facility's database and automate calculations for protocols using Excel and Filemaker, helping streamline the lab and more consistently produce and record valuable data. 
Furthermore, I am continually applying techniques I learned from a professional development course on project management for scientists across more than 12 projects to deliver high quality final products in a timely fashion to our partners.\par%\vspace*{3mm}

%As part of this transition, I quickly adapted and implemented new protocols for the production and quantification of viral vector tools in mammalian cell culture in addition to producing a number of genetic constructs via recombineering and other cloning strategies.
%Initially our two person team only provided recombinant AAV, but as my skills progressed, the scope of my portfolio has expanded to include recombinant lentivirus and we are in the process of adding HSV.
%In my position with EMBL I have expanded on my organizational skills and taken the initiative to extend the facility's database and automate calculations for protocols using Excel and Filemaker, helping streamline the lab and more consistently produce and record valuable data.
%Additionally, I am continually applying techniques I learned from a professional development course on project management for scientists across more than 12 projects to deliver high quality final products in a timely fashion to our partners.\par\vspace*{3mm}

Although EMBL offered extensive experience in the lab and provided room for growth, the research focus on neurobiology and epigenetics is simply not after my own heart.
Your lab offers the opportunity both to follow my passion to help make a sustainable and circular economy a reality. 
If you agree, I would appreciate the opportunity to discuss any potential position and my contributions in more detail. 
Thank you for your time and consideration, I look forward to hearing from you.

%For my theses {\href{https://www.ncbi.nlm.nih.gov/pubmed/29517395}{\textcolor{blue}{{\textit{(Publication)}}}}} I manipulated and analyzed algae (\textit{P. tricornutum}, \textit{N. ocecanica}) and cyanobacteria (Synechocystis sp. PCC6803). 
%More specifically, I used different transformation methods, analyzed their protein and RNA expression and explored the endogenous Synechocystis CRISPR-Cas system for appplication in metabolic engineering. 
%The wide array of lectures and courses I took in biochemistry, translational biology and microbiology has  left me with a solid foundation to learn and develop new procedures and protocols in the lab. 
%As an example, during a reorganization of my current lab, I consulted relevant literature to establish standard protocols for the production and quantification of viral vector tools in mammalian cell culture. 
%Due to the reshaping I also started working in a BSL2 environment and am aware of the importance of stringently following safety guidelines and maintaining a safe working environment. 
%Our facility currently only consists of my supervisor and me, meaning I not only produce high-quality viral vectors and genetic constructs independently, but also maintain a functional laboratory and took the initiative to improve the facility's database (FileMaker)---leaving me with excellent organizational skills I will invest to ensure accurate data recording and storage at the NBC.  
%I have also attended a professional course on presenting with impact and project management for scientists and am able to apply these techniques to balance multiple projects---currently more than 12 at once---while managing my time to deliver final products as quickly as possible.  \par%\vspace*{1mm}

%For the iGEM competition I participated in an interdisciplinary team of 20 highly motivated students.
%Within a month we agreed on an influential topic, and after only eight months of wet lab we produced high-value  {\href{https://www.ncbi.nlm.nih.gov/pubmed/29803867}{\textcolor{blue}{\textit{data}}}}, finally presenting our team's findings on our {\href{http://2015.igem.org/Team:Freiburg}{\textcolor{blue}{\textit{website}}}} and at an international conference. 
%This experience has not only left me with a strong work ethic, but also with the ability to efficiently identify the essentials from scientific findings and to present these in a comprehensive way to my team and a wider audience. 
%During this time we successfully ran our own lab independently, including ordering reagents, communicating with companies and funding agencies for financial or material aid, making and sterilizing media and keeping the lab and our data organized. \par

%Given my skill set I believe I could make valuable contributions to your team and it would be an honor to contribute to your research into algal biofuels. 
%If you agree, I would appreciate the opportunity to discuss any potential position and my contributions in more detail. 
%Thank you for your time and consideration, I look forward to hearing from you.


 

\end{spacing}
%\vspace*{1mm} 
\makeletterclosing
\end{document}