\documentclass[11pt,a4paper,sans]{moderncv}

\usepackage{float}
\usepackage{caption}
\usepackage{fancyhdr}
\usepackage{setspace}
\usepackage{verbatim}
\usepackage[scale=0.8, top = 1.8cm, bottom = 3cm]{geometry}

\moderncvstyle{casual}                             
\moderncvcolor{blue}                               


%%%% FIX THIS SO IT LOOKS NICER
\fancypagestyle{titlepage}{
\fancyhead{}
\fancyfoot[CE, CO]{\textcolor{gray}{Via Ramarini 32, 00015 Monterotondo, RM, Italy\thinspace\thinspace $\bullet$ \thinspace\thinspace\mobilephonesymbol +39~(388)~059~1507 \thinspace\thinspace $\bullet$ \thinspace\thinspace \faSkype \thinspace\thinspace \href{skype:rabea.jesser}{rabea.jesser} \thinspace\thinspace \thinspace\thinspace \emailsymbol \href{mailto:rabeajesser@web.de}{rabeajesser@web.de} \thinspace\thinspace $\bullet$ \thinspace\thinspace \faLinkedin \thinspace\thinspace \href{https://www.linkedin.com/in/rabeajesser/}{https://www.linkedin.com/in/rabeajesser/}}}}


\name{\vspace{-5mm}Rabea Jesser}{\vspace{3mm}}

\patchcmd{\makelettertitle}% <cmd>
  {\raggedright \@opening}% <search>
  {\parindent=11pt % or what you think best
   \parskip=0pt plus 0.1pt % remove the blank lines between paragraphs
   \@opening}% <replace>
  {}{}% <success><failure>


\begin{document}

%Adams Research Focus
%rapid screening of microalgae for photosynthetic efficiency and oil content
%Towards algal biofuels:  Enhancement of the production of energy-rich compounds by photosynthetic algae 
%comparing different ecotypes of Arabidopsis
%photosynthesis adaption to climate, limitations to capacity
%


%%%%%%%%%%%%% 			THOMAS NOTES 			%%%%%%%%%%%%%%%%%%%%%%%
% Just wanted to say, w.r.t. the above: If they are saying stuff that you don't have, try to highlight experiences
% where you were able to learn new techniques quickly. So they should be thinking: ``She's got most everything 
% we need and she is definitely smart enough to figure the rest out
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\thispagestyle{titlepage}

\recipient{Demmig-Adams and Adams group}{University of Colorado\\1900 Pleasant Street, CO 80309-0334}
%%%% DONT FORGET TO UPDATE THIS OR USE \today
\date{\today}
%%%%% IF YOU KNOW WHO YOU'RE SENDING THIS TO THEN GIVE THEIR NAME
\opening{Dear Dr. Demming-Adams and Dr. Adams,\vspace{-.5mm}}
\closing{Sincerely,}
\enclosure[Note]{Reference contacts and/or letters of reference will be sent upon request.}          
\makelettertitle
\begin{spacing}{1.2}


Interested in building on my existing experience with photosynthetic organisms and  their potential to help human society move away from a dependence on fossil fuels, I am applying for an upcoming position as a research technician with the Demming-Adams or Adams group. After studying alga in my bacherlor and successfully taking part in the iGEM (international Genetically Engineered Machine) competition, I worked with cyanobacteria in my masters degree. I am skilled in working with RNA, genetic engineering, producing viral vector tools and proteins and can quickly adapt to new challenges.\par\vspace{.75mm}

{\hskip 1em}During my bachelor thesis I gained insight into the cultivation of \textit{Nannochloropsis oceanica} and \textit{Phaeodactylum tricornutum} in the lab of Dr. Uwe Maier at the University of Marburg, Germany. For my master thesis I successfully cultivated and processed Synechocystis sp. PCC 6803 in the lab of Dr. Wolfgang Hess at the University of Freiburg, Germany {\href{https://www.ncbi.nlm.nih.gov/pubmed/29517395}{\textcolor{blue}{{\textit{(Publication)}}}}}. These experiences have left me well equipped to prepare and cultivate both algae and cyanobacteria. The wide array of lectures and courses in plant sciences, translational biology and microbiology has left me with a solid foundation to learn and develop new procedures and protocols in the lab. Within the first few months at EMBL my job description changed quite dramatically but I quickly adapted and implemented  techniques that were new to both my supervisor and me. With the reorganization I also started working in a BSL2 environment and am therefore aware of the importance of stringently following safety guidelines and maintaining a clean working environment. \par\vspace{.75mm}

{\hskip 1em}Taking part in iGEM in 2015 gave me the chance to both work independently and cooperate with an interdisciplinary team of 20 students. During iGEM I mostly focused on protein purification but also taught myself adobe illustrator, thereby generating most illustratory designs for our {\href{http://2015.igem.org/Team:Freiburg}{\textcolor{blue}{\textit{website}}}}, and got accutomed to using an internal wiki for accurate and reliable data storage. Partaking in iGEM and working in a facility honed my skills in organization and daily maintenance of running a lab.  At my current position I took the initiative to further develop and organize  the facility's database (FileMaker) - leaving me with excellent organizational skills I could invest to improve data recording and storage in your lab. I have also attended a professional course on presenting with impact and project management for scientists. I am able to apply these techniques to balance multiple projects at once while managing my time to keep ahead of deadlines. Additionally, a range of volunteering activities have honed my interpersonal, organizational and communication skills.\par\vspace{.75mm}

{\hskip 1em}Given my skillset I believe I could make valuable contributions to the Demming-Adams and/or Adams lab and it would be an honor to contribute to your research. If you agree, I would appreciate the opportunity to discuss a potential position and my skills in more detail. Thank you for your time and consideration, I look forward to hearing from you.


 

\end{spacing}
%\vspace*{1mm} 
\makeletterclosing

\end{document}