\documentclass[11pt,a4paper,sans]{moderncv}

\usepackage{float}
\usepackage{caption}
\usepackage{fancyhdr}
\usepackage{setspace}
\usepackage{verbatim}
\usepackage[scale=0.8, top = 1.6cm, bottom = 2cm]{geometry}

\moderncvstyle{casual}                             
\moderncvcolor{blue}                               


%%%% FIX THIS SO IT LOOKS NICER
\fancypagestyle{titlepage}{
\fancyhead{}
\fancyfoot[CE, CO]{\textcolor{gray}{Via Ramarini 32, Monterotondo RM, 00015 \thinspace\thinspace $\bullet$ \thinspace\thinspace\mobilephonesymbol +39~(388)~059~1507 \thinspace\thinspace $\bullet$ \thinspace\thinspace \faSkype \thinspace\thinspace \href{skype:rabea.jesser}{rabea.jesser} \thinspace\thinspace \thinspace\thinspace \emailsymbol \href{mailto:rabeajesser@web.de}{rabeajesser@web.de} \thinspace\thinspace $\bullet$ \thinspace\thinspace \faLinkedin \thinspace\thinspace \href{https://www.linkedin.com/in/rabeajesser/}{https://www.linkedin.com/in/rabeajesser/}}}}


\name{\vspace{-5mm}Rabea Jesser}{\vspace{3mm}}

\begin{document}

%MycoTechnology
%GOT MORE THAN THAT: Associates Degree required. Bachelor’s Degree is preferred.

% DON'T REALLY HAVE THAT BUT HAVE A MASTERS: 1-3 years of related experience, highly desirable. QA experience within the food manufacturing industry, preferred.

%GOT THAT: Knowledge of scientific principles and practices that provide the foundation for laboratory testing including: microbiology, chemistry.

%DON'T THINK I EXACTLY HAVE THAT: Knowledge of manufacturing processes, quality control principles and analysis techniques to maximize the effective manufacture and distribution of goods.

%TOTALLY GOT THAT: Excellent communication skills, both verbal and written

%HIGHLIGHT Establishment of WORK PRIORITIES (WEEKLY PLAN SEEABLE FOR ALL TEAM MEMBERS to GET THINGS DONE MOST EFFICIENTLY) : Demonstrated interpersonal skills, with special ability to work independently and establish work priorities with team members.

%HIGHLIGHT THIS IN ESTABLISHING PROTOCOLS: Critical thinking and decision-making skills to consider and identify the strengths and weakness of alternative solutions and chose the most appropriate course of action.

%GOT THAT: Ability to communicate information and ideas effectively and in a way that other Team Members will understand.

%GOT THAT: Ability to read and comprehend work instructions and work-related documents.

%OK, THAT'S NOT REALLY A REQUIREMENT: Must complete HACCP certification program within 12 months of hire.

%OK, THAT'S NOT REALLY A REQUIREMENT: Must complete PCQI Practitioner certification within 6 months of hire. 

%organic, mushroom based food enhancers, non-chemically, non-gmo


%%%%%%%%%%%%% 			THOMAS NOTES 			%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\thispagestyle{titlepage}

\recipient{Horizon Ag-Products, LP}{1450 Infinite Drive\\Louisville, CO 80027\vspace{-2mm}}
%%%% DONT FORGET TO UPDATE THIS OR USE \today
\date{\today}
%%%%% IF YOU KNOW WHO YOU'RE SENDING THIS TO THEN GIVE THEIR NAME
\opening{Dear MycoTechnology representative,\vspace{-2mm}}
\closing{Sincerely,\vspace*{-4mm} }
%\enclosure[Note]{Reference contacts and/or letters of reference will be sent upon request.}          
\makelettertitle
\begin{spacing}{1.15}

Given my dedication to quality, high attention to detail and critical-thinking skills, I would make an excellent addition to the MycoTechnology team as a QC Technician and relish the opportunity to help develop organic and natural food enhancers. After a B.Sc. in Biology and participation in the iGEM (international Genetically Engineered Machine) competition, I received a M.Sc. in Biology before working with the European Molecular Biology Laboratory (EMBL) in Rome. Across various research projects I have worked both independently and as part of a team, gaining strong problem-solving skills to refine the quality of procedures and products, precise attention to detail and excellent communication skills. Furthermore, my  experience in developing and executing protocols illustrates my ability to read, comprehend and apply instructions as well as my quick adaptation to new challenges and eagerness to learn. \par\vspace*{2mm}

During my B.Sc. thesis I worked with \textit{Nannochloropsis oceanica} and \textit{Phaeodactylum tricornutum} while for my M.Sc. thesis I cultivated Synechocystis sp. PCC 6803 {\href{https://www.ncbi.nlm.nih.gov/pubmed/29517395}{\textcolor{blue}{{\textit{(Publication)}}}}}. Through these experiences I developed excellent analytical and critical thinking skills and became well-versed in gathering, analyzing and recording scientific data. With a solid foundation in mycology  and an ability to analyze and adopt current literature practices I can analyze the strenghts and weaknesses of alternative options and take educated decisions. For instance, during a reorganization of my current lab, I consulted a variety of available protocols and methods to establish a procedure and SOPs and the necessary quality control for the production and quantification of viral vector tools in mammalian cell culture. In the process I got accustomed to  techniques that were new to both my supervisor and me. As a consequence I also began working in a BSL2 environment and am aware of the importance of stringently following safety guidelines to  maintain a clean, safe and efficient working environment, to meet or exceed all regulatory safetly and quality requirements and immediately report any issues to the health and safety manager.\par\vspace*{2mm}

Outside of the lecture hall, iGEM gave me the chance to cooperate within an interdisciplinary team of 20 students, to analyze and test the common work and refine the final product in a team effort. During iGEM it was essential to accurately record results comprehensively for all team members in an internal wiki to ensure consistent quality. To communicate ideas and findings clearly within the group and beyond I taught myself Adobe Illustrator and designed illustrations for our {\href{http://2015.igem.org/Team:Freiburg}{\textcolor{blue}{\textit{website}}}}. At my current position, I took the initiative to further develop the facility's database (FileMaker) and set up a weekly project schedule to establish work priorities in the team and guarantee the most efficient time use. I also attended a professional course on presenting with impact and project management for scientists and am able to apply these techniques to balance multiple projects at once while managing my time to keep ahead of deadlines. Finally, through a wide range of volunteering activities I have honed my interpersonal, organizational and communication skills, which will help in any situation whether organizing a lab or assisting in projects.\par\vspace*{2mm}

Working for Horizon as a research technician is a natural continuation of my experience, skills and passion in consistently delivering high quality biological products and I believe I could make valuable contributions to Horizon's R\&D team. If you agree, I would appreciate the opportunity to discuss the position and my skills in more detail. Thank you for your consideration, I look forward to hearing from you and will be following up next week.

\end{spacing}
\vspace*{2mm} 
\makeletterclosing
\end{document}


%During my bachelor's thesis I gained insight into the cultivation of \textit{Nannochloropsis oceanica} and \textit{Phaeodactylum tricornutum} in the lab of Dr. Uwe Maier. For my master thesis I successfully cultivated and processed Synechocystis sp. PCC 6803 in the lab of Dr. Wolfgang Hess {\href{https://www.ncbi.nlm.nih.gov/pubmed/29517395}{\textcolor{blue}{{\textit{(Publication)}}}}}. These experiences have left me well equipped to prepare, cultivate and manipulate both algae and cyanobacteria and analyze their genetic background as well as their transcriptional activity and screen for secondary metabolites. The wide array of lectures and courses I took in plant sciences, translational biology and microbiology has left me with a solid foundation to genetically alter different organisms, analyze and translate genetic pathways like CRISPR-Cas systems and implement published methods. More generally, I have a proven ability to quickly learn and develop new procedures and protocols as when, during a reorganization of the lab, I was tasked with establishing protocols for the production of viral vector tools in mammalian cell culture using techniques that were new to both my supervisor and me. During this time I also began working in a BSL2 environment and am aware of the importance of stringently following safety guidelines and maintaining a clean working environment.
%Taking part in iGEM gave me the chance to work both independently and within an interdisciplinary team of 20 students and to present our team's findings to an international audience. iGEM also gave me a chance to hone my skills in organization and the daily maintenance of running a lab, including ensuring the availability of reagents, approaching companies and funding agencies for financial or material aid, cleaning and sterilizing equipment and using an internal wiki for accurate and reliable data storage. My specific focus during iGEM was protein purification but I also taught myself adobe illustrator in order to generate higher quality designs for our {\href{http://2015.igem.org/Team:Freiburg}{\textcolor{blue}{\textit{website}}}}. At my current position, I took the initiative to further develop and organize the facility's database (FileMaker) - leaving me with excellent organizational skills I could invest to improve data recording and storage in your lab. I have also attended a professional course on presenting with impact and project management for scientists and am able to apply these techniques to balance multiple projects at once while managing my time to keep ahead of deadlines. Finally, through a wide range of volunteering activities I have honed my interpersonal, organizational and communication skills which will help in any situation whether in the lab or presenting at conferences.\par%\vspace*{1mm}


%Given my skillset I believe I could make valuable contributions to the Demming-Adams and/or Adams lab and it would be an honor to contribute to your research. If you agree, I would appreciate the opportunity to discuss a potential position and my skills in more detail. Thank you for your time and consideration, I look forward to hearing from you.


 

\end{spacing}
%\vspace*{1mm} 
\makeletterclosing
\end{document}